Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-04 paper/paper.tex
+ todo

\paragraph{Elements specific to control systems}
\cdsay{discussion on the noise introduced by the plant modelling?}
For stability, there are only two counterexamples, which are known. 
Thus, we can just enumerate them..
%\cdsay{Then, do we actually need program synthesis?}

\paragraph{Running example synthesis}

There are two different algorithms in DSVerifier that can be used for
stability verification, one based on Schur's decomposition and another
one based on Jury's criteria \cite{DBLP:journals/dafes/BessaICF16};
here, the Jury's method is chosen due to its efficiency.

@@

We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
Our goal is to synthesise ...
% Counterexample from first cruisecontrol02.c benchmark with uncertainty and
% nondeterminism:
% 1) { (0.02634525299072265625, 0.9979267120361328125, -0.99768829345703125) }
% 2) { (0.02644824981689453125, 1.00053310394287109375, -1.0014629364013671875) }

>>>>

\paragraph{Elements specific to control systems}
There are two different algorithms in DSVerifier that can be used for
stability verification, one based on Schur's decomposition and another
one based on Jury's criteria \cite{DBLP:journals/dafes/BessaICF16};
here, the Jury's method is chosen due to its efficiency.

@@

\paragraph{Running example synthesis}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
\cdsay{Pascal, I also need the candidate solutions here}
% Counterexample from first cruisecontrol02.c benchmark with uncertainty and
% nondeterminism:
% 1) { (0.02634525299072265625, 0.9979267120361328125, -0.99768829345703125) }
% 2) { (0.02644824981689453125, 1.00053310394287109375, -1.0014629364013671875) }
